On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-11-12 paper.tex
Joined two figures as subfigures of a single figure

For instance, it is clear from Figure~\ref{fig: examples} that segment orientations near the vertical or horizontal directions (resulting in $i=1$ with large $j$, or $j=1$ with large $i$) will not maximize the number of visited tiles, and thus the corresponding $(i,j)$ pairs can be discarded. On the other hand, the set of optimal $(i,j)$ pairs must contain one such pair for each possible value of $i+j-1$, so that the set can produce that value as the solution (maximum number of visited tiles) for certain lengths. It is insightful to examine two specific examples before giving an explicit formula for the coordinates of the optimal pairs.

@@

\begin{figure}
\centering%
\includegraphics[width=.7\textwidth]{ijLS_1}%
\caption{Relationship of segment length and number of visited tiles with the width and height of the discrete bounding rectangle, for $a=b$
}%
\label{fig: ijLS_1}%
\end{figure}%
% ***Maybe combine this figure and the next into one figure with two subfigures (stacked vertically, size similar to now). Not sure. It has been done in others

@@

\begin{figure}
\centering%
\includegraphics[width=.7\textwidth]{ijLS_1p35}%
\caption{Relationship of segment length and number of visited tiles with the width and height of the discrete bounding rectangle, for $a=1.35b$
}%
\label{fig: ijLS_1p35}%
\end{figure}%

@@

For \eqref{eq: probmax lim odd} it suffices to note that
\begin{align}
\label{eq: tedious limit, odd 1}
\lim_{\tiles \rightarrow \infty}\, \tiles g\left(\frac{\sqrt{(\tiles-3)^2+(\tiles-1)^2}} 2, \tiles-3, \tiles-3 \right) &= \frac 2 {3\pi} \\
\label{eq: tedious limit, odd 2}
\lim_{\tiles \rightarrow \infty}\, \tiles g\left(\frac{\sqrt{(\tiles-3)^2+(\tiles-1)^2}} 2, \tiles-5, \tiles-1 \right)
& = \frac 2 {3\pi},
\end{align}
as can be (somewhat tediously) checked using L'H\^opital's rule \cite[section~5.3]{Abbott15}.
%***I think. It's very tedious by hand. I used Maple to compute the limit, and then checked it numerically. Maybe one or two intermediate steps from applying L'H\^opital's rule should be included. Perhaps those can be obtained with Maple too, and this part can be rewritten.
Combining these expressions with the second equality in \eqref{eq: probmax} yields \eqref{eq: probmax lim odd}.

>>>>

For instance, it is clear from Figure~\ref{fig: examples} that segment orientations near the vertical or horizontal directions (resulting in $i=1$ with large $j$, or $j=1$ with large $i$) will not maximize the number of visited tiles, and thus the corresponding $(i,j)$ pairs can be discarded. On the other hand, the set of optimal $(i,j)$ pairs must contain one such pair for each possible value of $i+j-1$, so that the set can produce that value as the solution (maximum number of visited tiles) for certain lengths. It is insightful to examine two specific examples (Figure~\ref{fig: ijLS}) before giving an explicit formula for the coordinates of the optimal pairs.

@@

\begin{figure}
\centering%
\subfigure[$a=b$]{%
\label{fig: ijLS_1}
\includegraphics[width=.7\textwidth]{ijLS_1}%
}\\%
\centering%
\subfigure[$a=1.35b$]{%
\label{fig: ijLS_1p35}
\includegraphics[width=.7\textwidth]{ijLS_1p35}%
}%
\caption{Relationship of segment length and number of visited tiles with the width and height of the discrete bounding rectangle
}%
\label{fig: ijLS}%
\end{figure}%

@@

@@

For \eqref{eq: probmax lim odd} it suffices to note that
\begin{align}
\label{eq: tedious limit, odd 1}
\lim_{\tiles \rightarrow \infty}\, \tiles g\left(\frac{\sqrt{(\tiles-3)^2+(\tiles-1)^2}} 2, \tiles-3, \tiles-3 \right) &= \frac 2 {3\pi} \\
\label{eq: tedious limit, odd 2}
\lim_{\tiles \rightarrow \infty}\, \tiles g\left(\frac{\sqrt{(\tiles-3)^2+(\tiles-1)^2}} 2, \tiles-5, \tiles-1 \right)
& = \frac 2 {3\pi},
\end{align}
as can be (somewhat tediously) checked using L'H\^opital's rule \cite[section~5.3]{Abbott15}.
% It's very tedious by hand. I used Maple to compute the limit, and then checked it numerically. Maybe one or two intermediate steps from applying L'H\^opital's rule should be included. Perhaps those can be obtained with Maple too, and this part can be rewritten.
Combining these expressions with the second equality in \eqref{eq: probmax} yields \eqref{eq: probmax lim odd}.
